Identification of protoneutron star g-modes in gravitational-wave data

### 2020-07-14 methods.tex
add refs in methods.tex

Using 25 1D simulations obtained with the {\sc AENUS-ALCAR }code \cite{} and the
{\sc CoCoNuT} \cite{} code, we parametrize the ratio with a cubic polynomial
regression with heteroscedastic errors
%Here we are using the data from \textcolor{red}{only {\sc AENUS-ALCAR} or both?, maybe colour-code the two groups of data points } to fit a cubic polyn

@@

To develop the method we considered the gravitational wave signal
{\tt s20-gw-10kpc} described in Section \ref{sec:simulations}, originally
sampled at 16384 Hz but resampled at 4096 Hz.
A spectrogram of this signal is shown in Figure \ref{fig:spectrogram} based on
autoregressive estimates of the local spectra for successive time intervals of 
\textcolor{red}{length 200} with a \textcolor{red}{ 90\%} overlap.
The dominant emission mode corresponds to the $\mbox{}^2 g_2$-mode. We have
developed a time-frequency method to track the ridge $m(t)$ in the spectrogram,
taking into account that it is monotonically increasing as time goes,
a property of the $\mbox{}^2 g_2$-mode.
Starting from either the left- or right-most column of the time-frequency matrix
we identify and trace the sequence of amplitude peaks within a certain frequency
band given the monotonicity constraint. Appendix \ref{app:gmode} is providing more
details on the reconstruction of the $g$ mode ridge.

@@

We collect the instantaneous frequency $f(t_i)$ corresponding to the ridge $m(t_i)$ for
the midpoint $t_i$ of each local time interval of the spectrogram and interpolating $f(t)$
for values in between the $t_i$. We then use equation (\ref{eq:universal}) to obtain
estimates of the time evolution of the ratio together with 95\% confidence intervals.
An exemple is given in Figure \ref{fig:ratio} where the red points are the point estimates and
the grey bands represent 95\% confidence bands. The black points are the ratio values
computed using the mass and radius values obtained from the simulation code.

@@

In this case, for a GW signal without any noise, the coverage of our 95\% confidence band is 94\%.
In the next section we explore how accurately we can estimate $r(t)$ when the gravitational wave
signal is embedded in noise.

>>>>

Using 25 spherically symetric (1D) simulations obtained with the {\sc AENUS-ALCAR }code \citep{Just_et_al__2015__mnras__Anewmultidimensionalenergy-dependenttwo-momenttransportcodeforneutrino-hydrodynamics} and the
{\sc CoCoNuT} \citep{Cerda-Duran__2008__AA__GRMHD-code} code, we parametrize the ratio with a cubic polynomial
regression with heteroscedastic errors
%Here we are using the data from \textcolor{red}{only {\sc AENUS-ALCAR} or both?, maybe colour-code the two groups of data points } to fit a cubic polyn

@@

To develop the method we considered the gravitational wave signal
{\tt s20-gw-10kpc} described in Section \ref{sec:simulations}, originally
sampled at 16384 Hz but resampled at 4096 Hz.
A spectrogram of this signal is shown in Figure \ref{fig:spectrogram} based on
autoregressive estimates of the local spectra for successive time intervals of 
\textcolor{red}{length 200} with a \textcolor{red}{ 90\%} overlap.
The dominant emission mode corresponds to the PNS oscillation $\mbox{}^2 g_2$-mode. We have
developed a time-frequency method to track the ridge $m(t)$ in the spectrogram,
taking into account that it is monotonically increasing as time goes,
a property of the $\mbox{}^2 g_2$-mode.
Starting from either the left- or right-most column of the time-frequency matrix
we identify and trace the sequence of amplitude peaks within a certain frequency
band given the monotonicity constraint. Appendix \ref{app:gmode} is providing more
details on the reconstruction of the $g$ mode ridge.

@@

We collect the instantaneous frequency $f(t_i)$ corresponding to the ridge $m(t_i)$ for
the midpoint $t_i$ of each local time interval of the spectrogram and interpolating $f(t)$
for values in between the $t_i$. We then use equation (\ref{eq:universal}) to obtain
estimates of the time evolution of the ratio together with 95\% confidence intervals.
An exemple is given in Figure \ref{fig:ratio} where the red points are the point estimates and
the grey bands represent 95\% confidence bands. Ratio values
computed using the mass and radius values obtained from the simulation code are shown in black.

@@

In this case, for a GW signal without any noise, the coverage of our 95\% confidence band is 94\%.
In the next section we investigate the performance of reconstruction of $r(t)$ when the gravitational wave
signal is embedded in noise.
